\documentclass[english,11pt,a4paper,oneside]{article}
\usepackage[latin1]{inputenc}
\usepackage{babel}
\usepackage{amssymb}
\usepackage{currvita}
\usepackage{lipsum}
% \usepackage{texshade}
\usepackage{url}
% \usepackage{hyperref}
\usepackage[pdftex,                %%% hyper-references for pdflatex
bookmarks=true,%                   %%% generate bookmarks ...
bookmarksnumbered=true,%           %%% ... with numbers
hypertexnames=false,%              %%% needed for correct links to figures !!!
breaklinks=true,%                  %%% break links if exceeding a single line
linkbordercolor={0 0 1}]{hyperref}

%\usepackage{palatino}
\newcommand{\myurl}[1]{\footnote{\url{#1}}}
\usepackage{xspace}
\usepackage{color}

\newcommand{\via}{\emph{via}\xspace}
\newcommand{\ie}{\emph{i.e.}\xspace}
\newcommand{\eg}{\emph{e.g.}\xspace}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\todo}[1]{\textbf{{\color{blue}$\Longrightarrow$ #1}}}
% \newcommand{\todo}[1]{}


\begin{document}

\begin{cv}{Mikel Ega\~na Aranguren, Ph.D. }
% \todo{Learn how to toggle todo on and off for publishing}
 
 \begin{cvlist}{Background}
 	\item [Research statement:] My research area is Bioinformatics. I am interested in the exploitation of Semantic Web technology (RDF, OWL, automated reasoning, \etc) to improve knowledge management in Life Sciences. The realisation of this interest involves the development of semantic resources (Ontologies, Knowledge Bases, Linked Data datasets, Semantic Web Services, \etc) and the creation of tools for exploiting such resources.  
	 \item [Research keywords:] Bioinformatics, Life Sciences Semantic Web, Linked Data, Biomedical ontologies, (Meta) Genomics, Open Data, Identifiers, Beyond PDF, Beyond Impact Factor, Open Access, Free Software.
\end{cvlist}
 
\begin{cvlist}{Placements (Including funding) and education }

	
% \end{cvlist}
% 
% \begin{cvlist}{Placements (Including funding)}

% % % 	item RyC/ikerbasque/post-doc minneco txiki
% 	\item coordinador MSc
% 	\item visita seneca um
% 	\item mi plan nacional

	\item [4/2014-4/2015] Post-doc at the University of Basque Country (UPV-EHU), as a member of the Functional Genomics Group of the Department of Genetics, Physical Anthropology and Animal Physiology.

	\item [2/2011-2/2014] Post-doc at UPM (Spain) funded by Marie Curie Cofund (EU). Biological Informatics Group, Centre for Plant Biotechnology and Genomics (CBGP); Ontology Engineering Group, Computer Science Department.
% 	\item [\textbf{5/2012-2/2014}] \textbf{Marie Curie post-doc at Biological Informatics Group of CBGP, UPM, Spain.} 
% % 	[\href{http://wilkinsonlab.info/}{http://wilkinsonlab.info/}]	
% 	\item [2/2011-5/2012] Marie Curie post-doc at Ontology Engineering Group of Computer Science department, UPM, Spain.
% (UNITE 246565) 
	\item [11/2009-12/2009] Researcher in the OGO project at UM, Spain. Funded by the project ``Web platform for ontology-guided knowledge management in functional genomics'' (11/01/2007 to 10/01/2010), Autonomous Community of the Region of Murcia (BIO-TEC 06/01-0005).
% 	Member of the group TECNOMOD (Tecnolog\'ias de modelado, procesamiento y gesti\'on del conocimiento).
	\item [5/2006-10/2006] Researcher at Flanders Institute for Biotechnology (VIB), Belgium, funded by Marie Curie Early Stage Training (EST) by the EU. Member of the Computational Biology group of the Department of Plant Systems Biology.%MEST-CT-2004-414632
	\item [9/2005] Research visit to the European Bionformatics Institute (EBI), UK, to work with the Gene Ontology editors. Funded by the Network of Excellence on Semantic Interoperability and Data Mining in Biomedicine (EU).%FP6.507505
% 	\item [1/2005 - 7/2009] Ph.D. in Computer Science at University of Manchester, UK. Member of the Bio-Health Informatics Group.
	\item[1/2005-7/2009] Ph.D. in Computer Science at University of Manchester, UK, as a member of the Bio-Health Informatics Group, thesis title: ``Role and Application of Ontology Design Patterns (ODPs) in Bio-ontologies''.~External examiner: Michel Dumontier (Carleton University, Canada); Supervisor: Robert Stevens; Advisor: Alan Rector. Fees allowance by Engineering and Physical Sciences Research Council (EPSRC) and maintenance allowance by University of Manchester.
	\item[10/2003-9/2004] M.Sc.~in Bioinformatics at University of Manchester (UK). Distinction award for the thesis entitled ``Improving the structure of the Gene Ontology''.
	\item[6/2002] Evolutionary Ecology field course at Cardiff University, organised by Canterbury
	              Christ Church University College (UK).
	\item[9/2001-3/2002] Environmental Biology at Canterbury Christ Church University 
	                      College (UK) as Erasmus student.  
	\item[10/1997-9/2003] B.Sc. in Biology at University of Basque Country (EHU).
\end{cvlist}

% \begin{cvlist}{Projects}
% 	\item [11/2009-12/2009] Web platform for ontology-guided knowledge management in functional genomics (11/01/2007 to 10/01/2010). Autonomous Community of the Region of Murcia (BIO-TEC 06/01-0005). UM.
% \end{cvlist}

% \begin{cvlist}{Funding}
% 	\item [2/2011-2/2014] Marie Curie Cofund (UNITE 246565) by the EU: post-doc at UPM.
% 	\item [2005 - 2008] EPSRC and University of Manchester, UK: Ph.D. programme (Fees and maintenance).
% 	\item [5/2006 - 10/2006] Marie Curie Early Stage Training by the EU (MEST-CT-2004-414632): research at the VIB, Belgium.
% 	\item [9/2003 - 3/2004] Erasmus award by the EU: a semester in Canterbury Christ Church University College, UK.	
% \end{cvlist}

% http://tex.stackexchange.com/questions/54845/currvita-resume-section-without-bullets
\subsection*{Journal publications} %heading is wrong

\begin{itemize}



% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

% \item Jesualdo ortholog ontology
% 
% \item BIOM-LD GygaScience/JBMS/... 2014
% 
% \item mPuma Galaxy Microbiome/Microbial informatics and experimentation/PeerJ/... 2014
% 
% \item OpenLifeData2SADI JBMS 2014
% 
% \item PPIO SWJ 2014
% 
% \item SADI Galaxy JBMS 2014

% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!




\item Mikel Ega\~na Aranguren, Jesualdo Tom\'as Fern\'andez-Breis, Michel Dumontier. Special issue on Linked Data for Health Care and the Life Sciences (Editorial). \textit{Semantic Web Journal} 2014, 5(2): 99-100.

\item Jos\'e Antonio Mi\~narro-Gim\'enez, Mikel Ega\~na Aranguren, Boris Villaz\'on-Terrazas, Jesualdo Tom\'as Fern\'andez-Breis. Translational research combining orthologous genes and human diseases with the OGOLOD dataset. \textit{Semantic Web Journal} 2014, 5(2): 145-149.

\item Mikel Ega\~na Aranguren, Jesualdo Tom\'as Fern\'andez-Breis, Erick  Antezana, Chris Mu\-nga\-ll, Alejandro Rodr\'iguez Gonz\'alez, Mark D. Wilkinson. OPPL-Galaxy, a Galaxy tool for enhancing ontology exploitation as part of bioinformatics workflows. \textit{Journal of Biomedical Semantics} 2013, 4(1): 2. 

\item Astrid Duque-Ramos, Jesualdo Tom\'as Fern\'andez-Breis, Miguela Iniesta, Michel Dumontier, Mikel Ega\~na Aranguren, Stefan Schulz, Nathalie Aussenac-Gilles, Robert Stevens. Evaluation of the OQuaRE framework for ontology quality. \textit{Expert Systems with Applications} 2013, 40(7): 2696-2703. 

\item Jos\'e Antonio Mi\~narro-Gim\'enez, Mikel Ega\~na Aranguren, Boris Villaz\'on-Terrazas, Jesualdo Tom\'as Fern\'andez-Breis. Publishing Orthology and Diseases Information in the Linked Open Data cloud. \textit{Current Bioinformatics} 2012, 7(3): 255-266.

\item Vladimir Mironov, Erick Antezana, Mikel Ega\~na Aranguren, Ward Blond\'e, Bernard De Baets, Robert Stevens, Martin Kuiper. Flexibility and utility of the cell cycle ontology. \textit{Applied Ontology} 2011, 6(3): 247-261.

\item Jose Antonio Mi\~narro-Gimenez, Mikel Ega\~na Aranguren, Rodrigo Mart\'inez B\'ejar, Jesualdo Tom\'as Fern\'andez-Breis, Marisa Madrid. Semantic integration of information about orthologs and diseases: The OGO system. \textit{Journal of Biomedical Informatics} 2011, 44: 1020-1031.

\item Erick Antezana, Ward Blond\'e, Mikel Ega\~na Aranguren, Alistair Rutherford, Robert Stevens, Bernard De Baets, Vladimir Mironov, Martin Kuiper. BioGateway: a semantic systems biology tool for the life sciences. \textit{BMC bioinformatics} 2009, 10(Suppl 10): S11.

\item Erick Antezana, Mikel Ega\~na Aranguren, Ward Blond\'e, Aitzol Illarramendi, I\~naki Bilbao, Bernard De Baets, Robert Stevens, Vladimir Mironov, Martin Kuiper. The Cell Cycle Ontology: An application ontology for the representation and integrated analysis of the cell cycle process. \textit{Genome Biology} 2009, 10: R58.

\item Mikel Ega\~na Aranguren, Erick Antezana, Martin Kuiper, Robert Stevens. ODPs for bio-ontologies: a case study on the Cell Cycle Ontology. \textit{BMC bioinformatics} 2008, 9(Suppl 5): S1. 

\item Mikel Ega\~na Aranguren, Chris Wroe, Carole Goble, Robert Stevens. \textit{In situ} migration of handcrafted ontologies to Reason-able Forms. \textit{Data \& Knowledge Engineering} 2008, 66: 147-162.

\item Erick Antezana, Mikel Ega\~na Aranguren, Bernard De Baets, Martin Kuiper, Vladimir Mironov. ONTO-PERL: An API supporting the development and analysis of bio-ontologies. \textit{Bioinformatics} 2008, 24(6): 885-887.	

\item Mikel Ega\~na Aranguren, Sean Bechoffer, Phillip Lord, Ulrike Sattler, Robert Stevens. Understanding and using the meaning of statements in a bio-ontology: recasting the Gene Ontology in OWL. \textit{BMC Bioinformatics} 2007, 8: 57. 

\item Robert Stevens, Mikel Ega\~na Aranguren, Katy Wolstencroft, Ulrike Sattler, Nick Drummond, Mathew Horridge. Using OWL to Model Biological Knowledge. \textit{International Journal of Human Computer Studies} 2006, 65(7): 583-594.
\end{itemize}

\subsection*{Conference proceedings}

% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

% Add CBMS pdf to web 

% Add CBMS to scopus

% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

\begin{itemize}
       
       \item  Alejandro Rodr\'iguez Iglesias, Marcos Martinez Romero, Mikel Ega\~na Aranguren, Mark D. Wilkinson. Nanopublishing clinical diagnoses: tracking diagnostic knowledge base content and utilization. 27th IEEE International Symposium on Computer-Based Medical Systems (CBMS 2014): 335-340.

	\item Alejandro Rodr\'iguez Iglesias, Mikel Ega\~na Aranguren, Alejandro Rodr\'iguez Gonz\'alez, Mark D. Wilkinson. Plant-Pathogen Interactions Ontology (PPIO). IWBBIO 2013: 695-702.
	
	\item Mikel Ega\~na Aranguren, Jesualdo Tom\'as Fern\'andez-Breis, Erick Antezana. OPPL-Galaxy: Enhancing ontology exploitation in Galaxy with OPPL. SWA\-T\-4LS 2011, ACM 2012: 12-19.

	\item Jos\'e Antonio Mi\~narro-Gim\'enez, Mikel Ega\~na Aranguren, Francisco Garc\'ia-S\'anchez, Jesualdo Tom\'as Fern\'andez-Breis. A Semantic Query Interface for the OGO Platform. ITBAM (DEXA) 2010, LNCS 6266: 128-142.

	\item Mikel Ega\~na Aranguren, Alan Rector, Robert Stevens, Erick Antezana. Applying ODPs in bio-ontologies. EKAW 2008, LNCS 5268: 7-16.
\end{itemize}

\subsection*{Books and chapters in books}

\begin{itemize}



% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

% 	\item OWL spanish?
% 	
% 	\item Bioinformatika euskaraz?

% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!



	\item Mikel Ega\~na Aranguren, Robert Stevens, Erick Antezana, Jesualdo Tom\'as Fern\'andez-Breis, Martin Kuiper, Vladimir Mironov. Technologies and best practices for building bio-ontologies. In Alterovitz, G. and Ramoni, M., eds., \textit{Knowledge-based Bioinformatics: From Analysis to Interpretation}, 67-86. Wiley-VCH 2010, ISBN: 978-0-470-74831-2. 

% 	http://www.wiley-vch.de/publish/en/books/bySubjectST00/bySubSubjectST30/0-470-74831-1/?sID=r5gwqm31wqz3isk46oveaw5yag
% 	\item [2012] \todo{Introducci\'on a OWL. xxxx, ISBN 978-3-8433-7661-7. [\href{http://www.}{http://www.}]}  
	\item Role and application of ODPs in bio-ontologies. Lambert Academic Publishing 2010, ISBN 978-3-8433-7661-7. (Ph.D. thesis).
\end{itemize}

\subsection*{Publications in workshops and other publications}

\begin{itemize}
	\item Matthew Horridge, Mikel Ega\~na Aranguren, Jonathan Mortensen, Mark Musen, Natalya Noy. ODP language expressivity requirements. WOP 2012 (co-located with ISWC), Boston, USA. %http://ceur-ws.org/Vol-929/
	
	\item M. Scott Marshall, Richard Boyce, Helena F. Deus, Jun Zhao, Egon L Willighagen, Matthias Samwald, Elgar Pichler, Janos Hajagos, Mikel Ega\~na Aranguren, Eric Prud'hommeaux, Susie Stephens. \href{http://www.w3.org/2001/sw/hcls/notes/hcls-rdf-guide/}{Health Care and Life Science (HCLS) Linked Data Guide}. W3C note 2012.
% 	[\href{http://www.w3.org/2001/sw/hcls/notes/hcls-rdf-guide/}{http://www.w3.org/2001/sw/hcls/notes/hcls-rdf-guide/}] 
	
	\item Jose Antonio Mi\~narro Gim\'enez, Mikel Ega\~na Aranguren, Jesualdo Tom\'as Fern\'andez-Breis, Erick Antezana. NCBO-Galaxy: bridging the BioPortal web services and the Galaxy platform. Software demo at ICBO 2012, Graz, Austria.
	
	\item Publishing information in the LOD cloud. \href{http://bioinformatics.knowledgeblog.org}{Bioinformatics KnowledgeBlog} post.
	
	\item ``Automatic maintenance of multiple inheritance ontologies''; Review of ``Components of an Ontology''; Review of ``Reference and Application Ontologies''. \href{http://ontogenesis.knowledgeblog.org}{Ontogenesis KnowledgeBlog} posts 2011.
	
	\item Jesualdo Tom\'as Fern\'andez-Breis, Mikel Ega\~na Aranguren, Robert Stevens. A Quality Evaluation Framework for Bio-Ontologies. ICBO 2009, Buffalo, USA.
	
	\item Luigi Iannone, Mikel Ega\~na Aranguren, Alan Rector, Robert Stevens. Augmenting the expressivity of the Ontology Pre-Processor Language. OWLed 2008 Eu (co-located with ISWC), Karlsruhe, Germany.

	\item Mikel Ega\~na Aranguren, Robert Stevens, Erick Antezana. Transforming the Axiomisation of Ontologies: The Ontology Pre-Processor Language. OWLed 2008, Washington DC, USA.
	
	\item Antezana E, Blond\'e W, Mikel Ega\~na Aranguren, Rutherford A, Stevens R, De Baets B, Mironov V, Kuiper M: Structuring the life science resourceome for Semantic Systems Biology: lessons from the BioGateway project. SWAT4LS 2008, Edinburgh, Scotland, UK.
	
	\item ?`Qu\'e puede hacer la web sem\'antica por la biolog\'ia? BioGaia 7, 2007.
	
	\item Software libre (GNU/linux) para bi\'ologos. BioGaia 3, 2003.
	
	\item Cr\'itica a Linked Data en Open Data Euskadi (\href{http://mikeleganaaranguren.wordpress.com/2014/02/26/critica-a-linked-data-en-open-data-euskadi-ii-solucion/}{I y II}). Trabajo realizado en Open Data Day Deusto 2014 y citado en blog \href{http://opendata.blog.euskadi.net/blog-es/tecnico/779/}{Open Data Euskadi}. 
\end{itemize}
		
% \end{cvlist}

\subsection*{Posters}

\begin{itemize}

\item Sushil Tripathi, Aravind Venkatesan, Mikel Ega\~na Aranguren, Zahra Zavareh, Konika Chawla, Finn Drabl\o s, Liv Thommesen, Torunn Bruland, Vladimir Mironov, Martin Kuiper, and Astrid L\ae greid. Automated Assessment of High Throughput Hypotheses on Gene Regulatory Mechanisms Involved in the Gastrin Response. The 14th Annual Bio-Ontologies Meeting 2011, Vienna, Austria.

\item J.T. Fern\'andez-Breis, M.Madrid, J.A. Mi\~narro-Gim\'enez, M.C. Legaz-Garc\'ia, M. Ega\~na Aranguren, R. Stevens. Exploitation of Semantic Gene Ontology Annotations for Schizosaccharomyces Pombe. 6th International Fission Yeast Meeting 2011.

\item Antezana, E., Blond\'e, W., Ega\~na M., Stevens, R., De Baets, B., Mironov, V., Kuiper, M. The Cell Cycle Ontology: an application ontology supporting the study of cell cycle control. ICBO (International Conference on Biomedical Ontology) 2009, University at Buffalo, NY, US.

\item Antezana, E., Blond\'e, W., Ega\~na M., Rutherford, A., Stevens, R., De Baets, B., Mironov, V., Kuiper, M. BioGateway: an integrated RDF store to enable Semantic System Biology. ICBO (International Conference on Biomedical Ontology) 2009, University at Buffalo, NY, US.

\item Antezana, E., Blond\'e, W., Ega\~na M., Rutherford, A., Stevens, R., De Baets, B., Mironov, V., Kuiper, M. BioGateway: integrated RDF for life science queries. SWAT4LS - Semantic Web Applications and Tools for Life Sciences 2008, e-Science Institute, Edinburgh, Scotland, UK.

\item Antezana, E., Ega\~na M., Blond\'e, W., Stevens, R., De Baets, B., Mironov, V., Kuiper, M. The Cell Cycle Ontology: an application ontology supporting the Life Sciences. SWAT4LS - Semantic Web Applications and Tools for Life Sciences 2008, e-Science Institute, Edinburgh, Scotland, UK.

\item Antezana, E., Ega\~na M., Blond\'e, W., Mironov, V., Stevens, R., De Baets, B., Kuiper, M. The Cell Cycle Ontology: a step towards Semantic Systems Biology. EKAW 2008 - The 16th International Conference on Knowledge Engineering and Knowledge Management Knowledge Patterns. Acitrezza, Catania, Italy.

\item Antezana, E., Blond\'e, W., Ega\~na M., Stevens, R., De Baets, B., Mironov, V., Kuiper, M. BioGateway: enabling Semantic Systems Biology. MLSB08 - The 2nd International Workshop on Machine Learning in Systems Biology. Brussels, Belgium.

\item Antezana, E., Blond\'e, W., Ega\~na M., Stevens, R., De Baets, B., Mironov, V., Kuiper, M. Semantic Systems Biology: enabling integrative biology by semantic web technologies. The 9th International Conference on Systems Biology 2008. Gothenburg, Sweden.

\item Antezana, E., Ega\~na M., Stevens, R., De Baets, B., Mironov, V., Kuiper, M. The Cell Cycle Ontology: an application ontology for data integration. The 9th International Conference on Systems Biology 2008. Gothenburg, Sweden.

\item Antezana, E., Ega\~na M., Mironov, V., Kuiper, M. Ontology driven data integration for enabling systems biology. The 8th International Conference on Systems Biology 2007. Long Beach, California, US.

\item Antezana, E., Mironov, V., Ega\~na, M., and Kuiper, M. Ontology-driven Data Integration for Enabling Systems Biology: Cell-Cycle Ontology. The 4th Annual Integrative Bioinformatics Meeting 2007, Ghent, Belgium.

\item Antezana, E., Ega\~na, M., Mironov, V., and Kuiper, M. CCO, a paradigm for knowledge integration. The 10th Annual Bio-Ontologies Meeting 2007, Vienna, Austria.
\end{itemize}

% \begin{cvlist}{Other publications}

\subsection*{Editor}
	Semantic Web Journal (SWJ), special issue on Linked Data for Health Care and the Life Sciences. 
	Editors: Mikel Ega\~na Aranguren, Michel Dumontier, and Jesualdo Tom\'as Fern\'andez-Breis. 


\subsection*{Referee}
PeerJ (2013),
Data and Knowledge Engineering (DKE) (2013),
BMC Bioinformatics (2012),
Journal of Biomedical Informatics (JBI) (2012),
Computational and Mathematical Methods in Medicine (CMMM) (2012),
Journal of Medical Systems (JOMS) (2012),
Journal of Biomedical Semantics (JBS) (2012),
Semantic Web Journal (SWJ) (2011),
Journal of Research and Practice in Information Technology (JRPIT) (2011).

\subsection*{Member of scientific committee}
\begin{itemize}
	\item Managing Interoperability and compleXity in Health Systems (MIX-HS 2012). In conjunction with the ACM International Conference on Information and Knowledge Management. %http://informatics.mayo.edu/CNTRO/index.php/Events/MIXHS12
	\item Joint Workshop on Semantic Technologies Applied to Biomedical Informatics and Individualized Medicine (SATBI + SWIM 2012). In conjunction with International Semantic Web Conference (ISWC). % http://nadir.uc3m.es/satbi+swim2012/
	\item Managing Interoperability and compleXity in Health Systems (MIX-HS 2011). In conjunction with the ACM International Conference on Information and Knowledge Management. %http://informatics.mayo.edu/CNTRO/index.php/Events/MIXHS11#Programme_Chairs
	\item Additional reviewer in K-CAP (Knowledge Capture 2011). %http://kcap11.stanford.edu/
	\item Semantic Applied Technologies on Biomedical Informatics (SATBI 2011). In conjunction with the ACM International Conference on Bioinformatics and Computational Biology.  %(www.igsb.org/acm-bcb2011/)
	%(\href{http://nadir.uc3m.es/satbi2011/#ui-tabs-3}{http://nadir.uc3m.es/satbi2011/#ui-tabs-3}).
	\item ONTORACT 2008.
\end{itemize}

\subsection*{Talks}
\begin{itemize}
		\item Building reasonable biomedical ontologies for a Life Sciences Semantic Web. 3S (Systems, Synthetic, and Semantic) Biology summer school. CIBIO (Centre for Integrative Biology), University of Trento, Italy, 2014. Invited talk.
		\item OPPL-Galaxy: Enhancing ontology exploitation in Galaxy with OPPL. SWAT4LS, London, UK, 2011.
		\item Linked Data for Functional Genomics. NTNU, Trondheim, Norway, 2011. Invited talk.
		\item Publicar datos de manera inteligente en la Web: la filosof\'ia y la pr\'actica de los datos enlazados (Linked Data). Reuni\'on de la Red de Observatorios de Sostenibilidad. \'Evora, Portugal, 2011. 
		\item A Semantic Query Interface for the OGO Platform. ITBAM (DEXA), Bilbo, Spain, 2010.
		\item Aplicaci\'on de la Web Sem\'antica en Biolog\'ia Molecular. Universidad de Deusto, Facultad de Ingenier\'ia, Spain, 2010. Invited talk.
		\item Applying ODPs in bio-ontologies. EKAW, Catania, Italy, 2008.
		\item Transforming the Axiomisation of Ontologies: The Ontology Pre-Processor Language. OWLed, Washington DC, USA, 2008.
		\item Aplicaci\'on de la Web Sem\'antica en Bioinform\'atica. UM, Facultad de Inform\'atica, Spain, 2008. Invited talk.
		\item ODPs for bio-ontologies. Bio-ontologies SIG at ISMB, Vienna, Austria, 2007.
		\item M\'etodos y resultados actuales en Bioinform\'atica: know-how y know-what de las redes tecnocient\'ificas en Bioin-form\'atica. EHU, Facultad de Filosof\'ia, Spain, 2004. Invited talk.
\end{itemize}

\subsection*{Technical skills}
\begin{itemize}
	\item Semantic Web and Linked Data (Advanced): RDF, RDFS, SPARQL, OWL, SWRL, JSON-LD, OWL API, RDFLib, ONTO-PERL, Jena, Sesame, Stardog, Pubby, Prot\'eg\'e 4, TopBraid composer.
	\item Programming languages (Medium): Java, Perl, Python, Sed, Bash, JavaScript. 
	\item UNIX systems (Medium): GNU/Linux (Debian, Ubuntu, CentOS, Red Hat). 
	\item Markup languages (Medium): XML, HTML 5, \LaTeXe.
	\item Web Services (Basic): SADI framework, NCBO services.
	\item Web (Basic): Galaxy, Apache, Nginx, Tomcat, Jetty, lighttp, Solr/Lucene, Wordpress, Drupal, MarkDown, Jekyll.
	\item Software development (Basic): Maven, Ant, SCons, Eclipse, Subversion, Mercurial, Git, Trac.
	\item Teaching systems (Basic): Moodle.
	\item Relational Databases (Basic): MySQL, PostgreSQL.
% 	\item NoSQL Databases (Basic): BerkeleyDB ???
	\item File based data storage (Basic): HDF5, YAML, JSON.
	\item Statistical analysis (Basic): R.
	\item Cloud computing (Basic): Amazon EC2.
\end{itemize}

\begin{cvlist}{Participation in development of resources and tools}

% 	\item [Ortho-ontology ???]

% 	\item [biom-ld:] BIOM-LD is a mapping of the BIOM format (HDF5) to OWL (BIOMO) and RDF, in order to be able to semantically publish big metagenomics data.

	\item [OpenLifeData2SADI:] This a set of SADI services that wraps the Linked Data resources from Open Life Data (formerly known as Bio2RDF). 
% 	I wrote the Galaxy pipelines to demonstrate how to use the SADI services.
[\href{http://github.com/wilkinsonlab/OpenLifeData2SADI}{http://github.com/wilkinsonlab/OpenLifeData2SADI}]

	\item [DDx2NP:] This programme can be used to add Nanopublications to a given medical Knowledge Base. [\href{http://github.com/wilkinsonlab/DDx2NP}{http://github.com/wilkinsonlab/DDx2NP}]

	\item [SADI-Galaxy:] SADI-Galaxy is able to install SADI services as regular Galaxy tools, and therefore SADI services can be used as part of any Galaxy workflow. [\href{http://github.com/mikel-egana-aranguren/SADI-Galaxy}{http://github.com/mikel-egana-aranguren/SADI-Galaxy}]

	\item [LSLD:] This is a standalone, light-weight, configuration-free bundle to publish Linked Data. It is meant as an educational tool that students can use to become familiar with Linked Data, by publishing their own dataset at localhost with only the necessary hassle, but still being aware of the overal technical setting. It can also be used for rapid prototyping and deployment of a Linked Data system. [\href{http://github.com/mikel-egana-aranguren/LSLD}{http://github.com/mikel-egana-aranguren/LSLD}]
	
	\item [Linked Data Open Data Euskadi:] Este proyecto contiene el trabajo realizado en el Open Data Day Deusto 2014 por el grupo de trabajo ``Tutorial de Linked Data con ejemplo real de Open Data Euskadi''. Es un ``pack'', basado en LSLD, que puede ser desplegado en cualquier m\'aquina GNU/Linux y una vez funcionando demuestra la estructura y funcionamiento completo de un servidor Linked Data, con un dataset sobre consulados extra\'ido de Open Data Euskadi. [\href{http://github.com/OpenDataDayBilbao/Linked-Data-Open-Data-Euskadi}{http://github.com/OpenDataDayBilbao/Linked-Data-Open-Data-Euskadi}]

	\item [PPIO:] The Plant-Pathogen Interactions Ontology offers an axiomisation of plant-pathogen interactions in order to annotate, query and reason over such domain of knowledge. [\href{http://github.com/wilkinsonlab/PPIO}{http://github.com/wilkinsonlab/PPIO}]
	
	\item [PPIO software:] OWLNumericIDGenerator (Generate alphanumeric OWL URIs) and NCBITaxonomy2OWL (Import NCBI taxa from BioPortal Web Service) were written for producing PPIO. [\href{http://github.com/mikel-egana-aranguren/OWLNumericIDGenerator}{http://github.com/mikel-egana-aranguren/OWLNumericIDGenerator}] [\href{http://github.com/mikel-egana-aranguren/NCBITaxonomy2OWL}{http://github.com/mikel-egana-aranguren/NCBITaxonomy2OWL}]

	\item [NCBO-Galaxy:] NCBO-Galaxy provides graphical interfaces for the NCBO web services available at BioPortal, to access and exploit biomedical ontologies as part of Galaxy workflows. 
	[\href{http://toolshed.g2.bx.psu.edu/}{http://toolshed.g2.bx.psu.edu/}]	
	
	\item [OGO:] OGO integrates orthology information with diseases from OMIM, exploiting OWL, SPARQL and OBO ontologies. 
	[\href{http://miuras.inf.um.es:9080/OGO-1.0/}{http://miuras.inf.um.es:9080/OGO-1.0/}]

	\item [OGOLOD:] OGOLOD is the Linked Open Data version of the OGO system. 
	[\href{http://miuras.inf.um.es/~ogo/ogolod.html}{http://miuras.inf.um.es/\~{}ogo/ogolod.html}]

	\item [ODPs catalogue:] 
	A repository of ontology engineering best practices, focused on biological knowledge. 
	 [\href{http://github.com/mikel-egana-aranguren/ODPs}{http://github.com/mikel-egana-aranguren/ODPs}]
	
	\item [BioGateway:] 
	An RDF store holding information integrated from different bioinformatics resources, like the OBO ontologies, GOA files and SwissProt.
	[\href{http://www.semantic-systems-biology.org/biogateway}{http://www.semantic-systems-biology.org/biogateway}]
	
	\item [CCO:] 
	The Cell Cycle Ontology is an application ontology that describes different aspects of the cell cycle, integrating information from  UniProt, IntAct, GOA, NCBI taxonomy and GO. 
	[\href{http://cellcycleontology.org}{http://cellcycleontology.org}]

	\item [OPPL:] 
	The Ontology Pre-Processor Language is a scripting language for defining and performing axiomatic changes in OWL ontologies, thus offering an abstraction of the OWL API that works directly with axioms instead of programmatic procedures.
	 [\href{http://oppl.sourceforge.net/}{http://oppl.sourceforge.net/}]

	\item [OPPL-Galaxy:] OPPL-Galaxy is an OPPL wrapper to execute workflows that combine OPPL and other Galaxy tools to enhance the exploitation of biomedical ontologies in bioinformatics. [\href{http://github.com/mikel-egana-aranguren/OPPL-Galaxy}{http://github.com/mikel-egana-aranguren/OPPL-Galaxy}]
	 
	\item [ONTO-PERL:] 
	A Perl API for manipulating OBO and OWL ontologies. [\href{http://search.cpan.org/dist/ONTO-PERL/}{http://search.cpan.org/dist/ONTO-PERL/}]

	\item [GONG:] 
	Gene Ontology Next Generation is a methodology for enriching OBO ontologies by adding OWL axioms based on dissecting the structure of the term names with regular expressions. 
% 	[\href{http://www.gong.manchester.ac.uk}{http://www.gong.manchester.ac.uk}]
	
\end{cvlist}

\subsection*{Collaboration with research groups in publications}
\begin{itemize}
% 	\item MAthew Links?
% 	\item Chico navarro?
% 	\item Caporaso lab ???
	\item Biological Informatics Group. CBGP (UPM), Spain (2014). 
	\item Berkeley Bioinformatics Open-source Projects. Lawrence Berkeley National Laboratory, USA (2013).
	\item Methods and Engineering of Language, Ontology and DIscourse. Toulouse Institute of Computer Science Research, France (2013).
	\item Institute for Medical Informatics, Statistics and Documentation. Medical university of Graz, Austria (2013).
	\item Dumontier lab. Carleton University, Canada (2012).
	\item Bio-Medical Informatics Research Group. Stanford University, USA (2012).
	\item Isoco Labs. Isoco, Spain (2012).
	\item Noray bioinformatics, Spain (2009).
	\item Tecnolog\'ias de Modelado, Procesamiento y Gesti\'on del Conocimiento. Universidad de Murcia, Spain (2009).
	\item Semantic Systems Biology. Trondheim University, Norway (2008).
	\item KERMIT. Gent University, Belgium (2008).
	\item Information Management Group. University of Manchester, UK (2005).
	\item Bio-Health Informatics Group. University of Manchester, UK (2005).
\end{itemize}


\subsection*{Teaching}

\begin{itemize}

% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

% \item Scientific director of Bionformatics MSc by UPV/EHU (bioinformatika.info, bioinformatika.eu, http://mikel-egana-aranguren.github.io/EHU-MSc-Bioinformatics/, add link of github web to my web). ???


% \item Life Sciences Linked Data. Bioinformatics MSc, UPV-EHU, 2015. English. ???

% \item A lo loco. Bioinformatics MSc, UPV-EHU, UPV-EHU, 2015. English. ???

% !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!


\item Semantic biology tutorial: Use of semantic web resources for knowledge discovery. 3S (Systems, Synthetic, and Semantic) Biology summer school. CIBIO (Centre for Integrative Biology), University of Trento, Italy, 2014. English.
\item Galaxy tutorial. Erasmus mundus MSc in Marine Environment and resources, UPV-EHU, 2014. English.
\item Life Sciences Semantic Web. MSc Bioinformatics, UM, 2014. Spanish. %[\href{https://github.com/mikel-egana-aranguren/MSc_Bioinformatics_UM_13-14_LSSW}{Material}]
\item Introductory talk on bioinformatics for high school students visiting the CBGP.
\item Galaxy tutorials at CBGP. %[\href{http://github.com/mikel-egana-aranguren/Galaxy\_tutorial}{http://github.com/mikel-egana-aranguren/Galaxy\_tutorial}]

\item Life Sciences Linked Data. MSc Bioinformatics, UM, 2013. Spanish.
\item OWL, as part of ATHENS course (UPM), 2012. English.
\item OWL, as part of ATHENS course (UPM), 2012. English.
	
\item Populous tutorial at SWAT4LS (London, UK), 2011. English.
\item OWL, as part of ATHENS course (UPM), 2011. English.
\item Web Ontology Language (OWL), as part of Artificial Intelligence MSc (UPM), 2011. English. %(2 hours)
\item OWL/Description Logics, as part of the Artificial Intelligence course (UPM), 2011. Spanish. % (6 hours, 2 groups) 
% \item ANECA certificate: Ayudante Doctor.
\item OWL tutorials for biologists (University of Manchester, UK), 2005-2008. English.

%[\href{http://www.co-ode.org/resources/tutorials/bio/}{http://www.co-ode.org/resources/tutorials/bio/}]
\end{itemize}

\subsection*{Ph.D. Panels}
\begin{itemize}

	\item Meifania Monica Chen, ``Lipoprotein Ontology: A Formal Representation of Lipoproteins'', Curtin University, Australia, 2013. 

	\item Jose Antonio Mi\~narro-Gim\'enez, ``Entorno para la gesti\'on sem\'antica de informaci\'on biom\'edica en investigaci\'on traslacional'', UM, Spain, 2012. 

	\item Doris Mej\'ia \'Avila, ``Estrategia de interoperabilidad sem\'antica en el contexto de integraci\'on de conocimiento geogr\'afico y ambiental. Caso de aplicaci\'on: Biodiversity Ontology'', UPM, Spain, 2011. 
\end{itemize}

\subsection*{Memberships} 
W3C Semantic Web Health Care and Life Sciences Interest Group, Spanish Association of Linked Data, Biologists Association of Basque Country. 


\subsection*{Languages}
Fluent in english (IELTS 7.5/9), basque (EGA, HABE 3), and spanish.

% \begin{itemize}
% 	\item English: Fluent, IELTS band 7.5/9. 
% %	Practised in M.Sc., Ph.D., conferences, research visits and international projects.
% 	\item Basque: Native speaker: EGA, HABE 3. 
% %	Practised during B.Sc. in biology. 
% 	\item Spanish: Native speaker.	
% \end{itemize}



\begin{cvlist}{Scholar metrics}

	\item [Author ID Scopus: \href{http://www.scopus.com/authid/detail.url?authorId=16038705500}{16038705500}.
% 	\todo{If not merged, 16315598400, 36868687500, 16038705500, 54941280400}
]
	\item [Google Scholar profile: \href{http://scholar.google.com/citations?user=JsMMKnoAAAAJ}{JsMMKnoAAAAJ}.]
	\item [H-Index: 7 (Scopus), 12 (Google Scholar).]
	\item [Total Number of indexed publications: 15 (Scopus), 35 (Google Scholar).]
% 	\item \todo{Add PPIO IWBBIO to Scopus}
\end{cvlist}

\subsection*{Personal data}
\begin{itemize}
% 	\begin{small}
	\item Born 1979/8/26, in Bilbo (Basque Country, Spain).
	\item Web: 
% 			\begin{quote}
\href{http://mikeleganaaranguren.com}{http://mikeleganaaranguren.com}\footnote{Up-to-date CV, pointers to profiles (CiteUlike, GitHub, LinkedIn, \etc), links to publications, and other works (slides, theses, teaching materials, videos, \etc).}.

% \footnote{Expanded personal data, up-to-date CV, CV in other formats, developed resources, pointers to profiles (Scopus, Google Scholar, CiteUlike, GitHub, LinkedIn \etc), links to publications, and other works (slides, theses, teaching materials, videos, \etc).}



% 			\end{quote}
	\item Email: 
% 			\begin{quote}
			\href{mailto:mikel.egana.aranguren@gmail.com}{mikel.egana.aranguren@gmail.com} / \href{mailto:mikel.egana@ehu.es}{mikel.egana@ehu.es}. 
% 			ni@mikeleganaaranguren.com
			
% 			\end{quote}
	\item Skype: mikel\_egana. 
% 	\item Phone:  (0034) 656724785.
% 			/ 0044 (0) 7810165783
% 	\item Post:


% 			Jardines de Gernika 25 6B \\
% 			Bilbo 48003 \\
% 			Spain
% 	\end{small}
\end{itemize}

% \begin{cvlist}{References (available upon request)}
% Mark Wilkinson (CBGP, UPM, Spain),  Robert Stevens (University of Manchester, UK), Jesualdo Tom\'as Fern\'andez-Breis (UM, Spain).
% 	\item [Mark Wilkinson (CBGP, UPM, Spain).]	
% 	\item [Martin Kuiper (NTNU, Norway).]
% 	\item [Robert Stevens (University of Manchester, UK).]
% 	\item [Jesualdo Tom\'as Fern\'andez-Breis (UM, Spain).]
% 	\item [Asunci\'on G\'omez P\'erez (UPM, Spain).]
% 	\item [Oscar Corcho (UPM, Spain).]
% \end{cvlist}

% \begin{cvlist}{Other merits}
%  	\item [ISO 9001 quality management system: 30 hours course at UPV/EHU.]
%  	\item [Work-risks prevention: 30 hours course at UPV/EHU.]
%  	\item [UNIX administration: 30 hours course at UPV/EHU.] 	 
% 	\item [XML: 16 hours course at University of Deusto.]
% 	\item [Scuba diving license (PADI Open Water).]
% 	\item [Driving license (B).]
% \end{cvlist}


\cvplace{Bilbo}
\date{2014/08/27}

\end{cv}

\end{document}



 


%Web platform for ontology-guided knowledge management in functional genomics (11/01/2007 to 10/01/2010). Autonomous Community of the Region of Murcia (BIO-TEC 06/01-0005). Rodrigo Martinez Bejar, University of Murcia.

%\item [11/2009 - 12/2009] Web platform for ontology-guided knowledge management in functional genomics (11/01/2007 to 10/01/2010). Autonomous Community of the Region of Murcia (BIO-TEC 06/01-0005). Rodrigo Martinez Bejar, University of Murcia.	
%BIO-TEC 06/01-0005
%PLATAFORMA WEB PARA GESTIÓN DE CONOCIMIENTO GUIADA POR ONTOLOGÍAS EN GENÓMICA FUNCIONAL
%ENTIDAD: CONSEJERÍA DE EDUCACIÓN Y CULTURA. REGIÓN DE MURCIA.
%COMIENZO: 11/01/2007, FIN: 10/01/2010
%INV.RESP.: RODRIGO MARTINEZ BEJAR	
%	\item [5/2006 - 10/2006] DIAMONDS: Dedicated Integration And Modelling Of Novel Data
%and prior knowledge to enable Systems biology (1/1/2005 to 30/6/2008). 6th Framework Programme (LSHG-CT-2004-512143), Life Sciences, genomics and biotechnology for health. Martin Kuiper, VIB. 
%	\item [2005 - 2008] Ontogenesis (1/11/2006 to 31/4/2010). EPSRC. Robert Stevens, University of Manchester.
%	\item [2005 - 2008] Collaborative Open Ontology Development Environment (CO-ODE) (1/4/2003 to 30/9/2009). JISC. Alan Rector, University of Manchester.


% 	<li>Bioinformatics Knowledge Blog: This is a compilation of peer reviewed tutorials. [<a href="http://bioinformatics.knowledgeblog.org">http://bioinformatics.knowledgeblog.org</a>]</li>
% 	<li>Ontogenesis Knowledge Blog: This was an experiment on publishing papers about ontologies (Including peer review) using blogs, as part of the Ontogenesis network. [<a href="http://ontogenesis.knowledgeblog.org/">http://ontogenesis.knowledgeblog.org/</a>]</li>
