
%% http://theprofessorisin.com/2012/01/12/dr-karens-rules-of-the-academic-cv/

%% forked from https://github.com/cmungall/cv

\documentclass[11pt,fullpage]{article}

\usepackage{hyperref}
\usepackage{geometry}
%\usepackage{listliketab}
\usepackage{array}
\usepackage{longtable}

\usepackage{natbib}
\usepackage{bibentry}
\nobibliography*
%\bibliographystyle{apa}

% Palatino font
%\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}


\usepackage{xspace}
\usepackage{color}

\newcommand{\myurl}[1]{\footnote{\url{#1}}}
\newcommand{\via}{\emph{via}\xspace}
\newcommand{\ie}{\emph{i.e.}\xspace}
\newcommand{\eg}{\emph{e.g.}\xspace}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\todo}[1]{\textbf{{\color{blue}$\Longrightarrow$ #1}}}

\def\name{Mikel Ega\~na Aranguren, Ph.D.}

\reversemarginpar

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
%\sectionfont{\rmfamily\mdseries\Large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}
\bibliographystyle{apalike}

% Print name centered and bold:
\centerline{\Large \bf \name}

\vspace{0.25in}

\begin{minipage}{0.50\linewidth}
~\\
    Analyst, Torres Quevedo Fellow \\
    \href{http://eurohelp.es/}{Eurohelp Consulting} \\
  %  Bilbo, Spain \\



%   \href{http://www.genomic-resources.eu/}{Genomic Resources Group} \\
%   Dpt. of Genetics, Physical Anthropology and Animal Physiology \\
%   Faculty of Science and Technology \\
%   University of Basque Country (UPV/EHU) \\
%   Sarriena auzoa z/g \\
%   48940 Leioa - Bilbo, Spain \\

\end{minipage}
\begin{minipage}{0.50\linewidth}
  \begin{tabular}{ll}
%     Tel: & (0034) 946015503 \\
%    Skype: & mikel\_egana \\
%     Cell: & (0034) 656724785 \\
    Email: & \href{mailto:mikel.egana.aranguren@gmail.com}{mikel.egana.aranguren@gmail.com} \\
    Homepage: & \href{https://mikel-egana-aranguren.github.io}{https://mikel-egana-aranguren.github.io}

%     (Up-to-date CV, pointers to profiles (CiteUlike, GitHub, LinkedIn, \etc), links to publications, and other works (slides, theses, teaching materials, videos, \etc)) \\
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{tabular}{ll}
	2009 & {\bf Ph.D.} Computer Science, University of Manchester, UK \\
	2005 & {\bf M.Sc.} Bioinformatics, University of Manchester, UK \\
	2003 & {\bf B.Sc.} Biology, University of Basque Country, Spain \\
	2002 & {\bf Invited student} Evolutionary Ecology at Canterbury Christ Church University \\
	     & College, UK \\
	2002 & {\bf Erasmus student} Environmental Biology at Canterbury Christ Church University \\
	     & College, UK \\
\end{tabular}

\section*{Employment}

% Give institution, department, title, and dates (year only) of
% employment.  Be sure and reflect joint appointments if you have one

\begin{tabular}{ll}
 2016-Present & {\bf Analyst, Torres Quevedo fellow} Eurohelp Consulting \\
	      & Design and development of Linked Open Data solutions\\
 2015-2016 & {\bf Analyst} Eurohelp Consulting \\
	    & Design and development of Linked Open Data solutions\\
 2014-2015 & {\bf Post-doc researcher} Genomic Resources Group, UPV/EHU  \\
	  & Metagenomics and Life Sciences Semantic Web \\
 2011-2014 & {\bf Marie Curie Cofund fellow} Ontology Engineering Group (Computer \\
	    & Science); Biological Informatics Group (CBGP), UPM, Spain \\
	    & Ontology Engineering and Life Sciences Semantic Web \\
 2009 & {\bf Researcher} OGO project, UM, Spain \\
      & Orthologous Genes Ontology \\
 2006 & {\bf Marie Curie EST fellow} Computational Biology group, VIB, Belgium \\
     & Cell Cycle Ontology and Ontology Design Patterns \\
\end{tabular}

\section*{Research visits}

\begin{tabular}{ll}
 2005 & European Bioinformatics Institute (EBI), funded by the Network of Excellence on \\
      & Semantic Interoperability and Data Mining in Biomedicine (EU)

\end{tabular}

\section*{Funding obtained}

\begin{tabular}{ll}
%\begin{longtable}{p{0.5in}|p{5.5in}}
        2016-2018 & Torres Quevedo (Spain). 35\% of salary at Eurohelp Consulting. PTQ-14-07198 \\
	2011-2014 & Marie Curie Cofund (EU). UNITE 246565 \\
	2006 & Marie Curie EST (EU). MEST-CT-2004-414632 \\
	2005 & EPSRC (UK): Ph.D. fees \\
	2005 - 2008 & University of Manchester (UK): Ph.D. maintenance allowance \\
	2002 & Erasmus (EU) \\
%\end{longtable}
\end{tabular}

\section*{Participation in funded projects}

\begin{tabular}{ll}
  2017 - 2018 & SOLDAGE (Semantic Open Linked DAta GEnerator). HAZITEK, Gobierno Vasco. \\
              & FAIR data generator (150.000 EUR). \\
	2016 - 2017 & \href{http://www.contratacion.euskadi.eus/w32-1084/es/contenidos/anuncio_contratacion/expx74j21656/es_doc/es_arch_expx74j21656.html}{Servicios Open Linked Data}. EJIE (Sociedad Inform\'atica del Gobierno Vasco). \\
	            & Linked Data implementation of Open Data Euskadi (90.000 EUR). \\
        2016 - 2020 & REPLICATE. Renaissance of Places with Innovative Citizenship And \\
                    & TEchnology (Project 691735), EU. Linked Open Data in Smart Cities (\href{http://replicate-project.eu/}{http://replicate-project.eu/}). \\
                    & (Consortium: 24M EUR; Eurohelp: 300.000 EUR).  \\
        2015 - 2017 & Linking Open Domains, Plataforma para la generaci\'on de datos enlazados  \\
                    & (LODGen) (TSI-100105-2015-0012). Ministerio de Industria, Energia y Turismo (Spain), \\
                    & Acción Estratégica Economía y Sociedad Digital (AEESD) 1/2015.  \\
                    & Linked Open Data pipeline (40.000 EUR). \\
	2015 - 2016 & Enlazando Gipuzkoa con el Mundo (ENGIMU). Gipuzkoako Foru Aldundia,  \\
       & Gipuzkoa IKT: Innovación digital Empresas (Spain).\\
	     & Linked Open Data pipeline (40.000 EUR). \\
\end{tabular}

\section*{Publications}

\subsection*{Refereed Journal Articles}

\setlength{\extrarowheight}{10pt}

\begin{longtable}{p{0.5in}|p{5.5in}}
% Use: ./util/parsebib.pl article MyPubs.bib  | sort -r

 2015 & \bibentry{aranguren2015-gigascience} \\
 2015 & \bibentry{Pawluczyk-ABC} \\
 2014 & \bibentry{AleSr2014JBMS-OpenLifeData-SADI} \\
 2014 & \bibentry{aranguren2014JBMS-SADI-Galaxy} \\
 2014 & \bibentry{aranguren2014SWJ-ogolod} \\
 2014 & \bibentry{aranguren2014SWJ} \\
 2013 & \bibentry{oquare2013} \\
 2013 & \bibentry{EganaAranguren2013} \\
 2012 & \bibentry{minarro2012publishing} \\
 2011 & \bibentry{mironov2011flexibility} \\
 2011 & \bibentry{micnarro2011semantic} \\
 2009 & \bibentry{antezana2009cell} \\
 2009 & \bibentry{antezana2009biogateway} \\
 2008 & \bibentry{egana2008situ} \\
 2008 & \bibentry{aranguren2008ontology} \\
 2008 & \bibentry{antezana2008onto} \\
 2007 & \bibentry{stevens2007using} \\
 2007 & \bibentry{aranguren2007understanding} \\
\end{longtable}

\subsection*{Book Chapters}

\begin{longtable}{p{0.5in}|p{5.5in}}
% Use: ./util/parsebib.pl incollection MyPubs.bib  | sort -r
2010 & \bibentry{aranguren2010technologies} \\
\end{longtable}

\subsection*{Books}

\begin{longtable}{p{0.5in}|p{5.5in}}
% Use: ./util/parsebib.pl book MyPubs.bib  | sort -r
2010 & \bibentry{phd_mikel} \\
\end{longtable}


\subsection*{Conference Proceedings}
% Use: ./util/parsebib.pl inproceedings MyPubs.bib  | sort -r

\begin{longtable}{p{0.5in}|p{5.5in}}

 2014 & \bibentry{alesr2014} \\
 2013 & \bibentry{iwbbio2013} \\
 2011 & \bibentry{aranguren2011oppl} \\
 2010 & \bibentry{minarro2010semantic} \\
 2008 & \bibentry{ekaw2008} \\

\end{longtable}

\subsection*{Preprints, Workshop Proceedings and other publications}
% Use: ./util/parsebib.pl inproceedings MyPubs.bib  | sort -r
% Watch out for "OTHER-"

% Use: ./util/parsebib.pl misc MyPubs.bib  | sort -r

\begin{longtable}{p{0.5in}|p{5.5in}}
 2015 & \bibentry{OTHER-bioRxiv-SADI-Galaxy-Docker} \\
 2012 & \bibentry{OTHER-horridge2012ontology} \\
 2012 & \bibentry{OTHER-gimenez2012ncbo} \\
 2009 & \bibentry{OTHER-fernandez2009quality} \\
 2009 & \bibentry{OTHER-aranguren2009transforming} \\
 2008 & \bibentry{OTHER-iannone2008augmenting} \\
 2008 & \bibentry{OTHER-antezana2008structuring} \\
 2012 & \bibentry{OTHER-marshall2012w3c} \\
 2007 & \bibentry{OTHER-biogaia7}\\
 2003 & \bibentry{OTHER-biogaia3}
\end{longtable}



%\section*{Additional Papers Presented at Professional Meetings}

\section*{Invited Talks}

\begin{longtable}{p{0.5in}|p{5.5in}}

% Give title, institutional location, and date. Year only (not month
% or day) at left.  Month and day of talk go into entries.

2016 & Los Datos Enlazados y la Web Sem\'antica. Tikitalka, VE Interactive, Spain \\

2014 & Building reasonable biomedical ontologies for a Life Sciences Semantic Web. 3S (Systems, Synthetic, and Semantic) Biology summer school. CIBIO (Centre for Integrative Biology), University of Trento, Italy \\

2011 & Linked Data for Functional Genomics. NTNU, Trondheim, Norway \\

2010 & Aplicaci\'on de la Web Sem\'antica en Biolog\'ia Molecular. Universidad de Deusto, Facultad de Ingenier\'ia, Spain \\

2008 & Aplicaci\'on de la Web Sem\'antica en Bioinform\'atica. UM, Facultad de Inform\'atica, Spain \\

2004 & M\'etodos y resultados actuales en Bioinform\'atica: know-how y know-what de las redes tecnocient\'ificas en Bioinform\'atica. EHU, Facultad de Filosof\'ia, Spain

\end{longtable}


%\section*{Conference Activity}
% see below

% These entries will include: Name of paper, name of conference,
% date. Year (Year only) on left as noted above. Month and date-range
% of conference in the entry itself (ie, March 22-25).

\section*{Teaching Experience}

\begin{longtable}{p{0.5in}|p{5.5in}}

2017 & Life Sciences Semantic Web. MSc Bioinformatics, UM. Spanish \\
2016 & Life Sciences Semantic Web. MSc Bioinformatics, UM. Spanish \\
2016 & Linked Open Data tutorial. EJIE. Spanish \\
2015 & Linked Open Data tutorial. IZFE (Informatika Zerbitzuen Foru Elkartea, Gipuzkoa). Spanish \\
2015 & Life Sciences Semantic Web. MSc Bioinformatics, UM. Spanish \\
2014 & Semantic biology tutorial: Use of Semantic Web resources for knowledge discovery. 3S (Systems, Synthetic, and Semantic) Biology summer school. CIBIO (Centre for Integrative Biology), University of Trento, Italy. English \\
2014 & Galaxy tutorial. Erasmus mundus MSc in Marine Environment and resources, UPV-EHU. English \\
2014 & Life Sciences Semantic Web. MSc Bioinformatics, UM. Spanish \\ %[\href{https://github.com/mikel-egana-aranguren/MSc_Bioinformatics_UM_13-14_LSSW}{Material}]
2013 & Introductory talk on bioinformatics for high school students visiting the CBGP. Spanish \\
2013 & Galaxy tutorials at CBGP. English and spanish \\ %[\href{http://github.com/mikel-egana-aranguren/Galaxy\_tutorial}{http://github.com/mikel-egana-aranguren/Galaxy\_tutorial}]
2013 & Life Sciences Linked Data. MSc Bioinformatics, UM. Spanish \\
2012 & OWL, as part of ATHENS course (UPM). English \\
2012 & OWL, as part of ATHENS course (UPM). English \\
2011 & Populous tutorial at SWAT4LS (London, UK), English \\
2011 & OWL, as part of ATHENS course (UPM). English \\
2011 & Web Ontology Language (OWL), as part of Artificial Intelligence MSc (UPM). English \\ %(2 hours)
2011 & OWL/Description Logics, as part of the Artificial Intelligence course (UPM). Spanish \\ % (6 hours, 2 groups)
% \item ANECA certificate: Ayudante Doctor.
2005-2008 & OWL tutorials for biologists (University of Manchester, UK). English \\

\end{longtable}


\section*{Ph.D. panels}

\begin{longtable}{p{0.5in}|p{5.5in}}

2016 & Alejandro Rodr\'iguez Iglesias, ``FAIR approaches applied to unraveling plant-pathogen interactions data and RNA processing evolution'', UPM, Spain \\

2013 & Meifania Monica Chen, ``Lipoprotein Ontology: A Formal Representation of Lipoproteins'', Curtin University. Australia \\

2012 & Jose Antonio Mi\~narro-Gim\'enez, ``Entorno para la gesti\'on sem\'antica de informaci\'on biom\'edica en investigaci\'on traslacional''. UM, Spain \\

2011 & Doris Mej\'ia \'Avila, ``Estrategia de interoperabilidad sem\'antica en el contexto de integraci\'on de conocimiento geogr\'afico y ambiental. Caso de aplicaci\'on: Biodiversity Ontology''. UPM, Spain \\

\end{longtable}


\section*{Student supervision}

\begin{longtable}{p{0.5in}|p{5.5in}}

2017 & Denis Mishel Uchuari, internship at Eurohelp, Bachelor's Degree in Computer Engineering in Management and Information Systems. UPV/EHU, Spain \\
2015 &  Salvador Alonso Mart\'inez, ``Imagen Docker para pipelines de Metagen\'omica'', Bioinformatics MSc project. UM, Spain \\


\end{longtable}


\section*{Service}

% Include journal manuscript review work (with journal titles
% [mss. review CAN be given its own separate heading if you do a lot
% of this work]), leadership of professional organizations, etc. Some
% people put panel organizing under service; check conventions in your
% field.

\begin{longtable}{p{0.5in}|p{5.5in}}

2017 & \textbf{Chapter review} ``Integrating Biological Data using Semantic Web Technology'' in ``Evolutionary Genomics. computational and statistical methods'', 3rd edition, Springer. \\
2017 & \textbf{Program Committee Member} at Semantic Web Solutions for Large-Scale Biomedical Data Analytics (SeWeBMeDA 2017) \\
2015 & \textbf{Program Committee Member} at Linked Data workshop (CAEPIA 2015) \\
2015  & \textbf{Reviewer} for BMC Medical Informatics and Decision Making \\
2013 & {\bf Special issue editor} for Semantic Web Journal (SWJ): Special issue on Linked Data for Health Care and the Life Sciences \\
2013  & \textbf{Reviewer} for PeerJ \\
2013  & \textbf{Reviewer} for Data and Knowledge Engineering (DKE) \\

2012 & \textbf{Program Committee Member} at Managing Interoperability and compleXity in Health Systems. In conjunction with the ACM International Conference on Information and Knowledge Management\\
2012 & \textbf{Program Committee Member} at Joint Workshop on Semantic Technologies Applied to Biomedical Informatics and Individualized Medicine (SATBI + SWIM 2012). In conjunction with International Semantic Web Conference (ISWC)\\
2012  & \textbf{Reviewer} for BMC Bioinformatics \\
2012  & \textbf{Reviewer} for Journal of Biomedical Informatics (JBI) \\
2012  & \textbf{Reviewer} for Computational and Mathematical Methods in Medicine (CMMM) \\
2012  & \textbf{Reviewer} for Journal of Medical Systems (JOMS) \\
2012  & \textbf{Reviewer} for Journal of Biomedical Semantics (JBS) \\
2011 & \textbf{Program Committee Member} at Managing Interoperability and compleXity in Health Systems. In conjunction with the ACM International Conference on Information and Knowledge Management\\
2011 & \textbf{Program Committee Member} at Knowledge Capture (K-CAP)\\
2011 & \textbf{Program Committee Member} at Semantic Applied Technologies on Biomedical Informatics (SATBI 2011). In conjunction with the ACM International Conference on Bioinformatics and Computational Biology\\
2011  & \textbf{Reviewer} for Semantic Web Journal (SWJ) \\
2011  & \textbf{Reviewer} for Journal of Research and Practice in Information Technology (JRPIT)\\
2008 & \textbf{Program Committee Member} at ONTORACT \\

\end{longtable}


\section*{Collaboration with research groups in publications}

\begin{longtable}{p{0.5in}|p{5.5in}}

% Give title, institutional location, and date. Year only (not month
% or day) at left.  Month and day of talk go into entries.

2015 & Computer Science. University of Saskatchewan, Canada \\
2015 & Genetics. Technical University of Cartagena, Spain \\
2015 & Biological Informatics Group. CBGP (UPM), Spain \\
2014 & Biological Informatics Group. CBGP (UPM), Spain \\
2014 & Dumontier lab. Carleton University, Canada \\
2014 & Bio-Medical Informatics Research Group. Stanford University, USA \\
2013 & Berkeley Bioinformatics Open-source Projects. Lawrence Berkeley National Laboratory, USA \\
2013 & Methods and Engineering of Language, Ontology and DIscourse. Toulouse Institute of Computer Science Research, France \\
2013 & Institute for Medical Informatics, Statistics and Documentation. Medical university of Graz, Austria \\
2012 & Dumontier lab. Carleton University, Canada \\
2012 & Bio-Medical Informatics Research Group. Stanford University, USA \\
2012 & Isoco Labs. Isoco, Spain \\
2009 & Noray bioinformatics, Spain \\
2009 & Tecnolog\'ias de Modelado, Procesamiento y Gesti\'on del Conocimiento. Universidad de Murcia, Spain \\
2008 & Semantic Systems Biology. Trondheim University, Norway \\
2008 & KERMIT. Gent University, Belgium \\
2005 & Information Management Group. University of Manchester, UK \\
2005 & Bio-Health Informatics Group. University of Manchester, UK \\

\end{longtable}

\section*{Technical skills}
\begin{itemize}
	\item Semantic Web and Linked (Open) Data (Advanced): RDF, RDFS, SPARQL, OWL, SWRL, SHACL, JSON-LD, RDFa, OWL API, RDFLib, ONTO-PERL, Jena, RDF4J, Virtuoso, Stardog, Blazegraph, Apache Marmotta, GraphDB, Pubby, Prot\'eg\'e and Prot\'eg\'e server, TopBraid composer, CKAN, D2RQ, Open Refine, Grafter
	\item Programming languages (Medium): Java, Perl, Python
	\item Programming languages (Basic): Clojure, JavaScript, JSP, Bash, Groovy
  \item Markup languages (Basic): XML, XSLT, HTML
	\item UNIX systems (Medium): GNU/Linux (Debian, Ubuntu, CentOS, Red Hat)
	\item Markup languages (Medium): XML, HTML 5, CSS, \LaTeXe, MarkDown
	\item Web Services (Basic): SADI framework, NCBO services
	\item Web (Basic): Galaxy (Bioinformatics workflows), Apache, Nginx, Tomcat, Jetty, lighttp, Solr/Lucene, Wordpress, Drupal, Jekyll, NodeJS, Spring-MVC
	\item Software development (Basic): Maven, Ant, Leiningen, SCons, Eclipse, Subversion, Mercurial, Git, Travis CI, Jenkins, CodeCov
	\item Project management (Basic): Jira, Trac, Scrum, GitHub projects
	\item SQL and NoSQL Databases (Basic): MySQL, PostgreSQL, Neo4j
	\item File based data storage (Basic): HDF5, YAML, JSON
	\item Statistical analysis (Basic): R
	\item Cloud computing (Basic): Amazon EC2
	\item Virtualisation (Basic): Docker, Virtual Box
\end{itemize}

\section*{Learning experience}
\begin{longtable}{p{0.5in}|p{5.5in}}
2017 & Predictive modelling. One week course at \href{http://tecnalia.com/}{Tecnalia} \\
\end{longtable}

\section*{Other merits}
\begin{itemize}
	\item ANECA certificate: Ayudante Doctor
	\item Member of Open Knowledge Foundation Spain (OKFN-ES) and Basque Association of Biologists (COBE)
	\item Former member of the W3C Semantic Web Health Care and Life Sciences Interest Group and the Spanish Association of Linked Data (AELID)
\end{itemize}

\section*{Useful profiles}
\begin{itemize}
	\item GitHub: \href{http://github.com/mikel-egana-aranguren}{http://github.com/mikel-egana-aranguren}
	\item Google Scholar: \href{http://scholar.google.com/citations?user=JsMMKnoAAAAJ}{http://scholar.google.com/citations?user=JsMMKnoAAAAJ}
	\item Scopus: \href{http://www.scopus.com/authid/detail.url?authorId=16038705500}{http://www.scopus.com/authid/detail.url?authorId=16038705500}
	\item ResearchGate: \href{http://www.researchgate.net/profile/Mikel_Egana}{http://www.researchgate.net/profile/Mikel\_Egana}
	\item ORCID: \href{http://orcid.org/0000-0001-8081-1839}{http://orcid.org/0000-0001-8081-1839}
	\item ResearcherID: \href{http://www.researcherid.com/rid/K-6878-2014}{http://www.researcherid.com/rid/K-6878-2014}
\end{itemize}



% \section*{References}

% Give name and full title.


% Footer
\bigskip
\begin{center}
  \begin{footnotesize}
    Last updated: \today
  \end{footnotesize}
\end{center}



\nobibliography{MyPubs}
\end{document}
